---
title: "EDA: Romanian Weather during 2011 - 2021"
author:
- name: _Catalin-Gabriel Anastasiu (Gr 511)_
- name: _Serdal Aslantas (Gr 511)_
date: "_`r format(Sys.time(), '%d %B %Y')`_"
output: 
  html_document:
    highlight: pygments
    
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = TRUE, echo = TRUE, warning = FALSE)
```

## **1. The Data Set** 

### **1.1 Procuring the data**

In order to study the ways in which our country's weather has behaved in the
past years, we decided to look for a data set on different sources from the
Internet. Unfortunately, we have not found any data set containing the metrics
we need, therefore we decided to use a public API which would give us the
weather conditions in Romania in a set of locations and time periods we chose to
specify.

The period of time has been set to a daily basis from Jan 1st 2011, until Dec
31st 2021. This choice has been made due to financial limitations we encountered
on the API's part. In case that we had wanted to procure more data, more
requests would have been necessary to be made to the public API, exceeding the
threshold of free requests.

For each request, the API will return a single *.csv* file, respecting the name
convention "weather_YEAR_COUNTY.csv". So, for 41 Romanian counties and 11 years,
we would obtain 451 csv files. However, we need to work with a single data set,
so we decided to merge all of them into a single one in the code block below.

```{r}
library(tidyverse)

# TRUE only at first when "weather_2011-2021_Romania.csv" is not present in our project
MERGE_ALL_DATASETS = TRUE

if (MERGE_ALL_DATASETS) {
  
  filenames_list = list.files(
    path = "../weather_data/",
    pattern = "*.csv",
    full.names = TRUE
  )
  
  data = lapply(filenames_list, read_csv) %>% bind_rows()
  
  write.csv(data, "weather_2011-2021_Romania.csv", row.names = FALSE, na = "")
} 

data = read_csv("weather_2011-2021_Romania.csv", show_col_types = FALSE)
```

### **1.2 The data set's columns**

***TODO:*** Describe the meaning of each relevant column using [this documentation](https://www.visualcrossing.com/resources/documentation/weather-data/weather-data-documentation/)

## **2. EDA Chapter**


## **3. EDA Chapter **


## **4. EDA Chapter **


## **N. EDA Chapter **
